Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-24 paper/paper.tex
added battery details

Each airframe has nearly identical flight electronics. To power a Futaba 2.4GHz receiver and 6 servos for a XX minute flight, we selected a 2 cell XX amp hour Lithium Ion battery with a 5v, 10A capacity switching regulator made by Castle Creations. Pat will add more here if he has to.

>>>>

Each airframe has nearly identical flight electronics. To power a Futaba 2.4GHz receiver and 6 servos for a 20 minute flight, we selected a 2 cell (7.2v) 3.2 amp hour Lithium Ion battery with a 5v, 10A capacity switching regulator made by Castle Creations. We use a low voltage monitor in-line with the battery, which beeps when cell voltage falls below 7.2v. The autopilot electronics are powered off a completely separate battery for safety.
